Kids PM Summary

### 2021-01-21 manuscript_tables_figures.Rmd
New RMDs for intervention questionnaires

demographics <- read_rds(paste0(file_path, "Output/demographics_final.rds"))

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment_assigned == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(area, new_var) %>% 
  mutate(n = n(),
         percent = n()/area_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  select(new_var, n, percent) %>% 
  arrange(area, new_var)
demographics_summary
}

>>>>

demographics <- read_rds(paste0(file_path, "Output/demographics_final.rds")) %>% 
  filter(area == "WMT") %>% 
  filter(winter_id == 1) %>% 
  distinct(home_winter_id, .keep_all = TRUE)

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id == 1) %>% 
  #filter(treatment_assigned == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(area, new_var) %>% 
  mutate(n = n(),
         percent = n()/area_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  select(new_var, n, percent) %>% 
  arrange(area, new_var)
demographics_summary
}

### 2021-01-21 pm_summary.Rmd
New RMDs for intervention questionnaires

```{r, fig.height=4, fig.width=3}
boxplots_kids_pm <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  arrange(area, home, sampling_day) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  ggplot(aes(area, pm_mean_sampling_period)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red") +
    #scale_y_log10() +
    theme_minimal() +
    labs(title = "Red triangle = mean",
         y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black",
                                      margin = margin(t = 0, r = 0, b = 30, l = 0)),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm

ggsave("boxplots_kids_pm.jpg", height = 7, width = 4)
```

>>>>

```{r, fig.height=4, fig.width=3}
boxplots_kids_pm <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1) %>% 
  #filter(treatment_assigned == "Placebo") %>% 
  arrange(area, home, sampling_day) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  ggplot(aes(treatment_assigned, pm_mean_sampling_period)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red") +
    #scale_y_log10() +
    theme_minimal() +
    labs(title = "Red triangle = mean",
         y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black",
                                      margin = margin(t = 0, r = 0, b = 30, l = 0)),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm

#ggsave("boxplots_kids_pm.jpg", height = 7, width = 4)
```
